Project Uccle

### 2020-06-14 project.Rmd
slides v1

# Analysis
```{r whole data plot}
month.starts <- seq.POSIXt(from=floor_date(seis.h.start, 'month'), to=ceiling_date(seis.h.end, 'month'), by = "1 month")
hours.from.start <- as.numeric(month.starts-seis.h.start)*24+168
autoplot(seis.h.ts, type="l") +
  scale_x_continuous(breaks=hours.from.start/168, labels=format(month.starts, "%m-%y")) +
  ylab(data.lab) + xlab(NULL) + labs(title = "Training set", caption = "Data in original scale")
week.starts <- seq.POSIXt(from=floor_date(seis.h.start, 'week'), to=ceiling_date(seis.h.end, 'week'), by = "1 week")
hours.from.start <- as.numeric(week.starts-seis.h.start)*24+168
autoplot(seis.h.ts, type="l") +
  scale_x_continuous(breaks=hours.from.start/168, labels=format(week.starts, "%d-%m-%y"), limits = c(11,15)-3/24) +
  scale_y_continuous(limits = c(min(seis.h.ts[(10*168):(16*168)]), max(seis.h.ts[(10*168):(16*168)]))) +
  ylab(data.lab) + xlab(NULL) + labs(title = "Training set", subtitle = "4-weeks zoom", caption = "Data in original scale")
dec.addi <- decompose(seasonality.aggregate(seis.h.ts))
autoplot(dec.addi) + labs(title="Decomposition of additive time series", subtitle = paste0("Seasonality ", seasonality.period)) + xlab("Weeks")
```

@@

plot_grid(
  autoplot(seis.h.train, main = "Hourly seismic movement", xlab = seasonality.xlab, ylab = "mean movement (nm)"),
  gghistogram(seis.h.train, add.normal = T) + xlab("mean movement (nm)"),
  nrow = 2)
plot_grid(
  autoplot(acf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  autoplot(pacf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  nrow = 2)
```
Once notice the composition is additive (the fluctuations does not seem to grow with the trend)

@@

plots <- show_overlap_and_diff(
  dec.addi$trend, trend.s, xlab=seasonality.xlab,
  base.desc = "additive decomposition trend",
  compare.desc = paste0("shift-filtered trend with f=", f),
  overlap.ylab = "Trend (nm)",
  diff.title = "Difference between trends",
  diff.ylab = "nm", diff.ylab.sec="% over trend span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)

>>>>

# Analysis
```{r whole data plot}
month.starts <- seq.POSIXt(from=floor_date(seis.h.start, 'month'), to=ceiling_date(seis.h.end, 'month'), by = "1 month")
hours.from.start <- as.numeric(month.starts-seis.h.start)*24+168
autoplot(seis.h.ts, type="l") +
  scale_x_continuous(breaks=hours.from.start/168, labels=format(month.starts, "%m-%y")) +
  ylab(data.lab) + xlab(NULL) + labs(title = "Training set", caption = "Data in original scale")
week.starts <- seq.POSIXt(from=floor_date(seis.h.start, 'week'), to=ceiling_date(seis.h.end, 'week'), by = "1 week")
hours.from.start <- as.numeric(week.starts-seis.h.start)*24+168
autoplot(seis.h.ts, type="l") +
  scale_x_continuous(breaks=hours.from.start/168, labels=format(week.starts, "%d-%m-%y"), limits = c(11,15)-3/24) +
  scale_y_continuous(limits = c(min(seis.h.ts[(10*168):(16*168)]), max(seis.h.ts[(10*168):(16*168)]))) +
  ylab(data.lab) + xlab(NULL) + labs(title = paste("4-weeks zoom -", description), caption = "Data in original scale")
dec.addi <- decompose(seasonality.aggregate(seis.h.ts))
autoplot(dec.addi) + labs(title="Decomposition of additive time series", subtitle = paste0("Seasonality ", seasonality.period)) + xlab("Weeks")
```

@@

plot_grid(
  autoplot(seis.h.train, main = "Hourly seismic movement", xlab = seasonality.xlab, ylab = data.lab),
  gghistogram(seis.h.train, add.normal = T) + xlab(data.lab),
  nrow = 2)
plot_grid(
  autoplot(acf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  autoplot(pacf(seis.h.train, na.action=na.pass, plot=F, lag.max=seasonality.period)) + scale_x_continuous(),
  nrow = 2)
```
Once notice the composition is additive (the fluctuations does not seem to grow with the trend)

@@

plots <- show_overlap_and_diff(
  dec.addi$trend, trend.s, xlab=seasonality.xlab,
  base.desc = "additive decomposition trend",
  compare.desc = paste0("shift-filtered trend with f=", f),
  overlap.ylab = "Trend (nm)",
  diff.title = "Difference between trends",
  diff.ylab = "nm", diff.ylab.sec="% over trend span",
  diff.ylab.sec.accuracy = .01
)
plot_grid(plots[[1]], plots[[2]], nrow = 2)
autoplot(seis.h.train) +
  labs(title=paste("MA filtered trend -", description)) +
  scale_x_continuous(n.breaks=6, labels=function(x) format(seis.h.start + weeks(x-1), "%d-%m-'%y")) +
  geom_line(aes(y=trend.s, col="red"), show.legend=F) +
  ylab(data.lab)

### 2020-06-14 project.uccs.Rmd
slides v1

```{r set uccs, include=FALSE}
# UCCS
domain <- c(-350000,350000); pattern <- "UCCS-.+\\.csv"; name <- "UCCS"; description <- "Uccle, Bruxelles"; proj_file <- 'proj.uccs.RData'
```

>>>>

```{r set uccs, include=FALSE}
# UCCS
domain <- c(-350000,350000); pattern <- "UCCS-.+\\.csv"; name <- "UCCS"; description <- "Uccle, Brussels"; proj_file <- 'proj.uccs.RData'
```
